Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-10 rnni_convexity.tex
csort still needs details

\proof
Let $p$ be an arbitrary caterpillar path.
Every $\rnni$ move along $p$ can decrease the number of inversions of taxa in $T'$ and $R$ by either $1$ or $2$.
A decrease by $2$ is only possible when $T' = [x, y, z, \ldots]$, $z<\min(x,y)$, and the tree after the move is $[z, \min(x, y), \max(x, y), \ldots]$.
Hence $p$ is a shortest caterpillar path if every move along $p$ either is of this type or decreases the number of inversions by one.
Note that $\csort(T, R)$ satisfies this property.
\endproof

@@

The running time of $\csort$ is the same as for Bubble Sort, that is quadratic in $n$.

>>>>

\proof
Let $p$ be an arbitrary caterpillar path.
Every $\rnni$ move along $p$ can decrease the number of inversions of taxa in $T'$ and $R$ by either $1$ or $2$.
A decrease by $2$ is only possible when $T' = [x, y, z, \ldots]$, $z<\min(x,y)$, and the tree after the move is $[z, \min(x, y), \max(x, y), \ldots]$.
\todo{Explain why more moves that fix two inversion each are not possible.}
Hence $p$ is a shortest caterpillar path if every move along $p$ either is of this type or decreases the number of inversions by one.
Note that $\csort(T, R)$ satisfies this property.
\endproof

@@

The running time of $\csort$ is quadratic in $n$.
